### 2022-11-16 lmcs/priority-cp-long.tex
text for sec 4

>>>>

Thus far we have presented Priority GV (PGV) together with the relevant technical results. We remind the reader that this line of work of adding priorities, started with Priority CP (PCP) \cite{dardhagay18} where priorities are integrated in Wadler's Classical Processes (CP), which is a $\pi$-calculus leveraging the correspondence of session types as linear logic propositions \cite{wadler12}.
In his work, Wadler presents a connection (via encoding) of CP and GV. Following that work, we sat out to understand the connection between the priority versions of CP and GV, thus comparing PGV and PCP.
Before presenting our formal results, we will revisit PCP in the following section.
